Summary Tables

### 2019-04-11 summary_tables.Rmd
Update the titles of the tables @rahuliitd the delhi duration table does not look right. Looking into it.

for(city in cities){
    td <- io[[city]]$dist %>% mutate_if(is.numeric, round, digits = round_to)
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Distance table for ", city)))
    cat("\n")
}

@@

for(city in cities){
    td <- io[[city]]$dur %>% mutate_if(is.numeric, round, digits = round_to)
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Duration table for ", city)))
    cat("\n")
}

>>>>

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dist %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, funs(round((.) / count_people, round_to)))
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Distance table (km) for ", city, "( ", count_people, " ) per person")))
    cat("\n")

}

@@

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
    td <- io[[city]]$dur %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, funs(round((.) / count_people, round_to)))
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person")))
    cat("\n")
}
